---
title: "QTM151Lab01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## qplot()

The function *qplot()* in the package 'ggplot2' is very similar to the basic *plot()* function from the R base package. It can be used to create and combine easily different types of plots, it's great for allowing you to produce plots quickly, However, it remains less flexible than the function ggplot(), I highly recommend using *ggplot()* as it makes it easier to create complex graphics.

This lab provides a brief introduction to *qplot()*, which stands for quick plot. 



 Import the dataset:
```{r}
tips<-read.csv("tips.csv")
summary(tips)
```

#### Ex1: Histogram

```{r}
ggplot(tips, aes(x=tip))+
  geom_histogram(binwidth = 0.2)
```

qplot():
```{r}
#qplot(variables, geometry, color, size, shape, facet, dataset)
qplot(tip, geom = "histogram", binwidth=0.3, data=tips)

# add  blue color to the histogram
qplot(tip, geom = "histogram", binwidth=0.3, color="blue", data=tips)
# aesthetic parameters in qplot() always try to map the aesthetic to a variable, blue is a factor now

# Use I(value) to indicate a specific value
qplot(tip, geom = "histogram", binwidth=0.3, fill=I("blue"), data=tips)

# set color according to the variable sex
qplot(tip, geom = "histogram", binwidth=0.3, fill=sex, data=tips)

```


#### Ex2: Scatterplot 
```{r}
ggplot(tips, aes(x=totbill, y=tip))+
geom_point()+
  geom_smooth(method="lm")
```


```{r}
qplot(totbill, tip, geom="point", data=tips)

qplot(totbill, tip,  data=tips, color=I("red")) # qplot() gives a scatterplot by default

qplot(totbill, tip,  data=tips, color=sex)
```

add more geom arguments by a vector of multiple geom names in turn

```{r}
qplot(totbill, tip, geom = c("point","smooth"), data=tips)

qplot(totbill, tip, geom = c("point","smooth"), method="lm", data=tips)

# separate regression line for different sex
qplot(totbill, tip, geom = c("point","smooth"), method="lm", formula=y~x, color=sex, data=tips)

#no intuitive way to have just 1 line with two different colors, use ggplot for this
#y~x fits y axis to x axis


```

add labels 
```{r}
qplot(totbill, tip, geom = c("point","smooth"), data=tips, xlab="Total bill", ylab="Tip", main="Scatterplot")
```





#### Ex3: Side-by-side boxplot

```{r}
ggplot(tips, aes(x=sex, y=tip))+
  geom_boxplot()

# qplot
qplot(sex, tip, geom="boxplot", data=tips)


# add color to the variable sex
qplot(x=sex, y=tip, geom = "boxplot", fill=sex, data=tips)

qplot(x=sex, y=tip, geom = "boxplot", fill=I("blue"), data=tips)
```


#### Ex4: Add more factors by facets

```{r}
ggplot(tips, aes(x=sex, y=tip))+
geom_boxplot()+
 facet_grid(~time)

#qplot

qplot(sex, tip, geom="boxplot", facets=~time, data=tips) 



# add another variable smoker, set the color to the variable sex

qplot(sex, tip, geom = "boxplot", facets = time ~ smoker, data=tips)

```

```{r}

qplot(totbill, tip, geom = c("point","smooth"), method="lm", formula=y~x, facets=~day, color=sex, data=tips)

```







